A Kochen-Specker system has at least 21 vectors\\ {\small (extended abstract)}

### 2014-09-18 paper/main.tex
paper: remove superfluous line

\section{Conclusion and future research}
Arends, Ouaknine and Wampler struggled with two problems:
enumerating candidate graphs of less than 31 vertices
and testing their embeddability.
We have verified most of their computations.
Then we enumerated all candidate graphs
up to and including 21 vertices.
Furthermore, we have proposed a new decision procedure,
which was able to decide embeddability
for all candidate graphs we found.
Therefore, we demonstrate: a Kochen-Specker system must have at least
22 points.
At the time of writing,
we are computing
whether there is a KS system of 22 vertices.\footnote{
The authors have a wager whether there is a minimal KS system of less
than 25 vertices.}

>>>>

\section{Conclusion and future research}
Arends, Ouaknine and Wampler struggled with two problems:
enumerating candidate graphs of less than 31 vertices
and testing their embeddability.
We have verified most of their computations.
Then we enumerated all candidate graphs
up to and including 21 vertices.
Furthermore, we have proposed a new decision procedure,
which was able to decide embeddability
for all candidate graphs we found.
Therefore, we demonstrate: a Kochen-Specker system must have at least
22 points.\footnote{%
The authors have a wager whether there is a minimal KS system of less
than 25 vertices.}
